On the Gravitational stability of gravito-turbulent accretion disks

### 2016-03-22 paper/linear3d.tex
submitted version

\section{Linear problem}\label{linear}
We consider infinitestimal axisymmetric Eulerian perturbations of the
form \begin{align}
  \delta \rho= \widetilde{\delta \rho}(z)\exp{\left(\ii kx +
    s t\right)},  
\end{align}
and equivalent form for other variables. Here, $k$  is an input real horizontal
wavenumber and $s$ is a (generally) complex growth rate.  
For simplicity, hereafter we drop the tilde.

@@

Note that any linearized beta cooling function can be put into the
form of Eq. \ref{linear_beta} with appropriate definitions of $t_c$
and $\theta$ (see \S\ref{ppd_cooling} for an example).    
For the stability problem we may simply regard $\theta$ as a parameter 
for the density-dependence of any generic beta cooling function. If 
we specifically consider standard beta cooling, then $\theta$ also
represents physical irradiation.

>>>>

\section{Linear problem}\label{linear}
We consider infinitesimal axisymmetric Eulerian perturbations of the
form \begin{align}
  \delta \rho= \widetilde{\delta \rho}(z)\exp{\left(\ii kx +
    s t\right)},  
\end{align}
and equivalent form for other variables. Here, $k$  is an input real horizontal
wavenumber and $s$ is a (generally) complex growth rate.  
For simplicity, hereafter we drop the tilde.

@@

Note that any beta cooling function can be linearized in the
form of Eq. \ref{linear_beta} with appropriate definitions of $t_c$
and $\theta$ (see \S\ref{ppd_cooling} for an example).    
For the stability problem we may simply regard $\theta$ as a parameter 
for the density-dependence of any generic beta cooling function. If 
we specifically consider standard beta cooling, then $\theta$ also
represents physical irradiation.
